\textsf{Are large language models superhuman chemists?}

### 2024-10-24 src/tex/ms.tex
fix typo

In the subfield of analytical chemistry the prediction of the number of signals observable in a \gls{nmr} spectrum proved difficult for even for the best models (e.g., \variable{output/subset_scores/is_number_nmr_peaks_o1.txt} percent correct answers for \oone).
Importantly, while the human experts are given a drawing of the compounds, the models are only shown the \gls{smiles} string ofa a compound and have to use this to reason about the symmetry of the compound (i.e., to identify the number of diasterotopically distinct protons, which requires \emph{reasoning} about the topology and structure of a molecule).

>>>>

In the subfield of analytical chemistry the prediction of the number of signals observable in a \gls{nmr} spectrum proved difficult for even for the best models (e.g., \variable{output/subset_scores/is_number_nmr_peaks_o1.txt} percent correct answers for \oone).
Importantly, while the human experts are given a drawing of the compounds, the models are only shown the \gls{smiles} string of a a compound and have to use this to reason about the symmetry of the compound (i.e., to identify the number of diasterotopically distinct protons, which requires \emph{reasoning} about the topology and structure of a molecule).
